Synaptic connectome of the ctenophore apical organ

### 2025-02-17 manuscript/Manuscript.qmd
Materials and Methods
Fig6 legend

```{r, out.width = "100%", fig.cap="**Figure 6. Title fig 6** pic of a larva, boxed region of AO, schematic, catmaid pic with slice, dimensions, quadrants, regions, (A) legend (B) legend. " }
#| echo: false

knitr::include_graphics("figures/Figure6.png")
```

@@

### Cell Nomenclature and Annotations

### Analysis of Balancer Cilia

@@

### Volume electron microscopy

### Imaging of balancer activity

### Cell-type annotation and connectome analysis

### Data and code availability

>>>>

![**Figure 6. Comparison of Neural Circuits Regulating Ciliary Movement in *M. leidyi* (Ctenophore) and *P. dumerilii* (Annelid)**\
Each neuron represented by a circle is color-coded to indicate putative homologous cell types involved in ciliary movement regulation. Ciliated cells are shown in gray. Synapses are indicated by arrows, with magenta representing synapses that induce ciliary arrest and blue representing synapses that induce ciliary re-beat or an increase in ciliary beating frequency.\
(A) Gravity-sensing neural circuit of *M. leidyi*, as revealed in this study. Bridge cells (yellow squares) are suggested to be electrically coupled (indicated by yellow zigzag lines), implying their potential involvement in feedback mechanisms between neurons and ciliated cells.\
(B) Neural circuit regulating prototroch ciliary movement in *P. dumerilii*. Serotonergic neurons (Ser-h1 neurons, blue) activate ciliary movement, while cholinergic neurons (MC neurons, magenta) induce ciliary arrest. Arrows directed toward ciliated cells in the head prototroch are color-coded accordingly.](figures/Figure6.png)

@@

@@

### Cell-type Nomenclature, Annotations and Connectome Analysis

### Imaging of Balancer Cilia activity
